---
title: "Compliance and Sustainability Report (GRI)"
subtitle: "Bokitas Data Intelligence Project: From Legacy to Intelligence"
author: "Data Science and Cybersecurity Department"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    highlight: tango
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
library(tidyverse)
```

# 1. Introduction and Purpose (GRI 102)

This report documents the technical and ethical transition of the **Bokitas Ver 2.6** health control system to a modern data architecture. The process is governed by the **GRI 203 (Indirect Economic Impacts)** standard by strengthening community health infrastructure and the **GRI 418 (Customer Privacy)** standard by ensuring the protection of sensitive beneficiary data.

# 2. Forensic Data Archaeology (Phase 1)

Forensic engineering was performed on a legacy Visual FoxPro database, rescuing the relational integrity of historical operations.

### Inventory of Rescued Tables
| Module | Legacy Table | Records | Critical Function |
| :--- | :--- | :--- | :--- |
| **Nutritional** | `tb_antropometrica` | 528 | Longitudinal measurement tracking |
| **Socioeconomic** | `tb_socioeconomico` | 221 | Graffar Stratification |
| **Clinical** | `tb_pediatrica` | 412 | Medical diagnosis and treatment |
| **Reference** | `tb_pesotalla...` | 1,200 | WHO Standards (SD-3 to SD+3) |

# 3. Linear Processing Methodology (Tidyverse)

Historical data normalization was designed using functional programming principles to ensure reproducibility.

```{r cleaning-logic}
# Simulation of cleaning and consolidation of Master Data
master_data <- tb_antropometrica %>%
  inner_join(tb_menores, by = "cedula") %>%
  mutate(
    fecha_cons = as.Date(fecha_ini),
    peso_kg = as.numeric(peso),
    talla_cm = as.numeric(talla)
  ) %>%
  filter(!is.na(peso_kg) & talla_cm > 0) %>%
  select(cedula, fecha_cons, peso_kg, talla_cm, sexo, edad_meses)
```

# 4. Impact Indicator Calculation (GRI 203)

## 4.1. Anthropometric Analysis (WHO Anthro)
Following **WHO (2006)** guidelines, the system integrates Z-Score calculations to determine the standard deviation of the population.

```{r z-score-calc}
# Logic integration with WHO standard
library(anthro)

indices_nutri <- anthro_zscores(
  sex = master_data$sexo,
  age = master_data$edad_meses,
  weight = master_data$peso_kg,
  lenhei = master_data$talla_cm
)

# Binary classification for management reports
master_data <- master_data %>%
  mutate(dnt_aguda = ifelse(indices_nutri$zwei < -2, "Alert", "Normal"))
```

## 4.2. Socioeconomic Stratification (Graffar)
The data engine applies the **Graffar-Méndez Castellano** method to cross-reference social vulnerability with nutritional status.

```{r graffar-logic}
# Assignment of scores by housing and education variables
social_summary <- tb_socioeconomico %>%
  group_by(estrato) %>%
  summarise(
    total_beneficiaries = n(),
    risk_rate = mean(puntaje > 15)
  )
```

# 5. Privacy Shielding and GRI 418

In compliance with the **GRI 418-1** standard, a strict anonymization protocol was implemented before any cloud environment synchronization.

### Mitigation Actions Performed
- **Anonymization:** Replacement of real ID numbers and names with unique alphanumeric identifiers (UUIDs).
- **Isolation:** Physical removal of original `.DBF` files from the Git-tracked repository.
- **Dynamic Security:** Implementation of `.env` environment variables for database credentials.

# 6. Technical Assurance (Certification)

> #### TECHNICAL DISCLAIMER
> **It is certified that this repository is free of Personally Identifiable Information (PII).** All data contained in the development folders (`mock_data/`) is synthetic and does not correspond to real individuals. The Git history has been audited to ensure no residual metadata from the legacy archaeology phase exists.

---

**Signature:**  
*Lead Data Scientist & Compliance Officer*  
*Bokitas Data Intelligence Project*
